---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MMRFVariantPackage

<!-- badges: start -->
<!-- badges: end -->

The goal of MMRFVariantPackage is to analize variants from MMRF-CoMMpass dataset.

## Installation

Once R (version > “4.0”) has been started, you can install the released version of MMRFVariantPackage from GitHub with:

``` r
devtools::install_github("marziasettino/MMRFVariantPackage", build_vignettes = TRUE)
library(MMRFVariantPackage)
```

## Required libraries


```{r eval=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(DT)
library(ggplot2)
library(stringr)
library(ggpubr)
```


## Vignettes
A list of all currently integrated vignettes can be obtained through:




```{r eval=FALSE, message=FALSE, warning=FALSE}
vignette(package="MMRFVariantPackage")
```
The best way to view vignettes is in your web browser:


```{r eval=FALSE, message=FALSE, warning=FALSE}
devtools::load_all(".")
browseVignettes("MMRFVariantPackage")
```

Get the list of the example data sets

```{r eval=FALSE, message=FALSE, warning=FALSE}
data(package = "MMRFVariantPackage")
```

