---
title: "MMRFVariantPackage - Introduction"

package: MMRFVariantPackage
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{1. Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning=FALSE, 
  message=FALSE,
  comment = "#>"
)
```






```{r setup}
library(MMRFVariantPackage)
```


```{r, echo = FALSE,hide=TRUE, message=FALSE,warning=FALSE}
devtools::load_all(".")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(DT)
library(ggplot2)
library(stringr)
library(ggpubr)
```

## Introduction
<div class="panel panel-info">
<div class="panel-body">
<p align="justify">
MMRF-CoMMpass data can be retrieved directly from [MMRF-Commpass Researcher Gateway](https://research.themmrf.org/)
The user can download this dataset from MMRF-Commpass Researcher Gateway importing it as a dataframe into R environment.
</p>

</div>
</div>

### Get MMRF-COMMPASS data at MMRF-CoMMpass Research Gateway

<p align="justify">
In this example we will fetch  MMRF-CoMMpass information data from MMRF-COMMPASS Research Gateway. Once the dataset (.csv files) is imported into our own R environment, it is can be explored  as a R-dataframe.
</p>

```{r results = 'hide', message=FALSE, warning=FALSE, eval = F}

patient <- read.csv("~/MMRF_CoMMpass_IA15_PER_PATIENT")
trt <- read.csv("~/MMRF_CoMMpass_IA15_STAND_ALONE_TRTRESP")
variant.ann <- read.csv("~/MMRF_CoMMpass_IA15a_All_Canonical_Variants")


```


### Examples of MMRF-COMMPASS dataframe
  

<div class="panel panel-info">
<div class="panel-heading"><b>Annotated variant dataframe</b></div>
<div class="panel-body">
</div>
</div>
<p align="justify">
In order to test the provided functionalities without fetch  MMRF-CoMMpass information data from MMRF-COMMPASS Research Gateway, we provide the fictitious datasets:<br>

- <variant.ann.example> <br>
- <patient.example> <br>
- <trt.example> <br>

In this case, you should comment the previous code that fetches the MMRF-CoMMpass datasets (.csv files) from MMRF-COMMPASS Research Gateway 
</p>




```{r  echo=TRUE, message=FALSE, warning=FALSE}
datatable(variant.ann.example,options = list(scrollX = TRUE, keys = TRUE))

```

<div class="panel panel-info">
<div class="panel-heading"><b>Patient dataframe</b></div>
<div class="panel-body">
</div>
</div>
```{r  echo=TRUE, message=FALSE, warning=FALSE}
datatable(patient.example,options = list(scrollX = TRUE, keys = TRUE))

```


<div class="panel panel-info">
<div class="panel-heading"><b>Treatment dataframe</b></div>
<div class="panel-body">
</div>
</div>
```{r  echo=TRUE, message=FALSE, warning=FALSE}
datatable(trt.example,options = list(scrollX = TRUE, keys = TRUE))

```







